Income and Food Price Transmission\footnote{Revised version of MS 2015310 ``Income and Price Transmission''. Submitted to \emph{Agricultural Economics} for 2. round review. I thank two anonymous reviewers for their valuable comments.}

### 2016-02-29 Master.Rnw
Master file for 2. round version of paper.

\documentclass[12pt,english]{article}

\usepackage{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{babel}
\usepackage{url}
\usepackage{graphicx}
\usepackage{setspace}
\usepackage[authoryear]{natbib}
\usepackage[unicode=true]{hyperref}
\usepackage[format=hang, justification=raggedright]{subfig}
\usepackage{array}
\usepackage{multirow}
%\usepackage{authblk}
\usepackage{lscape}
\usepackage{float}
\usepackage{longtable}
\usepackage[noae]{Sweave}
\usepackage{setspace}
\doublespacing
\geometry{verbose,tmargin=2cm,bmargin=2cm,lmargin=3cm,rmargin=3cm}

@@

\title{Income and Food Price Transmission\footnote{Revised version of ``Poverty and Price Transmission''. Submitted to \emph{Agricultural Economics} for review}}

\author{Christian Elleby}
\date{2015}

\maketitle
\begin{abstract}
The paper analyzes how international-to-domestic food price transmission
depends on a country\textquoteright s income or expenditure level.
According to conventional wisdom, international food price spikes
have the largest poverty impact on low income countries. However,
the paper presents empirical evidence of an inverse-U shaped relationship
between the degree of international agricultural price changes passed
on to domestic consumers and the country\textquoteright s per capita
income or expenditure level. This implies that retail food prices
in middle income countries respond the strongest to international
commodity price spikes, whereas those in low income countries respond
less, all else equal. The specification of the empirical model is
based on a simple theoretical model of a country\textquoteright s
aggregate food price level. Its predictions are tested on monthly
price index data from 140 countries covering the six year period 2005-11
and results are found to be generally significant and robust. Around
one third to one half of the countries in the sample are to the left
of the turning point, on the increasing part of the parabola, in most
specifications.\end{abstract}

\SweaveInput{intro.Rnw}

\SweaveInput{litrev.Rnw}

\SweaveInput{model.Rnw}

\SweaveInput{analysis.Rnw}

\SweaveInput{conclusion.Rnw}

\bibliographystyle{chicago}
\bibliography{poverty_price_transmission}

\newpage

\appendix

\SweaveInput{figures.Rnw}

\newpage

\SweaveInput{tables.Rnw}

>>>>

\documentclass[12pt,english]{article}
\usepackage{color,soul}
\usepackage[T1]{fontenc}
\usepackage{inputenc}
\usepackage{babel}
\usepackage{url}
\usepackage{graphicx}
\usepackage[authoryear]{natbib}
\usepackage[unicode=true]{hyperref}
\usepackage[format=hang, justification=raggedright]{subfig}
\usepackage{array}
\usepackage{multirow}
\usepackage{lscape}
\usepackage{float}
\usepackage{longtable}
\usepackage{array}
\usepackage[noae]{Sweave}
\usepackage{setspace}
\doublespacing
\usepackage{geometry}
\geometry{verbose,tmargin=2cm,bmargin=2cm,lmargin=3cm,rmargin=3cm}
\usepackage{amsmath}
\usepackage[flushleft]{threeparttable}

@@

\title{Income and Food Price Transmission\footnote{Revised version of MS 2015310 ``Income and Price Transmission''. Submitted to \emph{Agricultural Economics} for 2. round review. I thank two anonymous reviewers for their valuable comments.}}

\date{\vspace{-5ex}}

\maketitle

\begin{abstract}
This paper examines determinants of international-to-domestic food price transmission using aggregate monthly price data for more than 100 countries covering the ten year period 2005-15. Findings indicate that middle-income countries experience the highest rates of food price transmission in the long run. Other determinants of food price transmission include a country's cereal import, export and consumption shares, its trade openness, the quality of its infrastructure and government involvement in grain trade. A novel model is presented which is able to explain the economic logic behind the observed inverse-U shaped relationship between income and price transmission.

\end{abstract}

\textbf{Keywords:} price transmission, food crisis, food inflation, determinants, regression analysis, income\newpage

\SweaveInput{intro.Rnw}
\SweaveInput{model.Rnw}
\SweaveInput{analysis.Rnw}
\SweaveInput{conclusion.Rnw}

\bibliographystyle{chicago}
\bibliography{inc_pt}

\SweaveInput{figures1.Rnw}
\newpage
\SweaveInput{tables.Rnw}
\newpage
\appendix
\SweaveInput{appendix.Rnw}
